### 2019-01-30 abstract.tex
ssr

\vspace*{-0.05in}
\begin{center}
\textbf{Abstract}~~ \textcolor{red}{\textbf{(To be revised)}}
\end{center}

@@

A class of Boolean functions, 
called \textbf{nested canalyzing functions} (NCFs),
has been used to model certain biological phenomena.
Rearchers have studied some properties of these functions
such as sensitivity and stability.
In this note, we examine the relationships between NCFs and symmetric 
Boolean functions. 
We identify all NCFs that are also symmetric. 
We also consider a more general form of symmetric Boolean functions
called $r$-symmetric functions, where $r$ is the symmetry level.
We show how one can get lower and upper bounds on the symmetry
level of an NCF $f$ given a suitable respresentation of $f$.

>>>>

\vspace*{-0.05in}
\begin{center}
\textbf{Abstract}  %% ~~ \textcolor{red}{\textbf{(To be revised)}}
\end{center}

@@

A class of Boolean functions, 
called \textbf{nested canalyzing functions} (NCFs),
has been used to model certain biological phenomena.
Researchers have studied some properties of these functions
such as sensitivity and stability.
In this note, we examine the relationships between NCFs and symmetric 
Boolean functions. 
We identify all the Boolean functions that both  NCFs and symmetric. 
A more general form of symmetric Boolean functions,
called $r$-symmetric functions (where $r$ is the symmetry level),
have also been studied in the literature.
%% We establish lower and upper bounds on the symmetry
%% level of an NCF $f$ as functions of the number of layers
%% in a standard respresentation of $f$.  
We show that, in general,
one cannot efficiently approximate the symmetry level of
a Boolean function to within any factor, unless \textbf{P} = \cnp. 
In contrast, we show that the symmetry level of an NCF $f$
can be easily computed from a standard (and efficiently
computable) representation of $f$.

### 2019-01-30 intro.tex
ssr

\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
\underline{\textsf{Generalized NCFs:}}~
For some problems, we will also consider a more general form
of NCFs defined below.

@@

\noindent
\textbf{Note:} If a generalized NCF is not a constant, 
there is an assignment to its variables
such that the value of the function is 0,
and there is an assignment to its variables
such that the value of the function is 1.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\fi

>>>>

\noindent
\underline{\textsf{Generalized NCFs:}}~
We will also consider a more general form of NCFs defined below.

@@

%% \bigskip

%% \noindent
%% \textbf{Note:} If a generalized NCF is not a constant, 
%% there is an assignment to its variables
%% such that the value of the function is 0,
%% and there is an assignment to its variables
%% such that the value of the function is 1.
